---
title: "2018 Mass Shooting Data Report"
output: html_document
---

```{r setup, include=FALSE}
source("scripts/analysis.R")
source("scripts/make_map.R")
source("scripts/make_bar_graph.R")
source("scripts/summary_table.R")
library("dplyr")
library("ggplot2")
library("leaflet")
knitr::opts_chunk$set(echo = TRUE)
```

## Summary Information
Unfortunately, the USA consistently has the most number of mass shootings per year compared to nations all across the globe. Guns and mass shooters have taken the lives of so many victims, and the year 2018 was no exception. There were a total number of `r total_shootings` mass shootings that occurred in 2018. A total number of `r lives_lost` lives were lost in these shootings. The most impacted city (aka the city with the highest mass shooting death toll) was `r most_impacted_city`. The most impacted state (aka the state with the highest mass shooting death toll) was `r most_impacted_state`. And finally, the city with the highest number of people injured due to mass shootings was `r most_injured_city`. The data I used to calculate these occurrences can be found at this link: http://www.shootingtracker.com/ (specifically the 2018 dataset)

## Summary Table

```{r echo=FALSE}
library(knitr)
cleaned_data_table <- read.csv("data/shootings_2018.csv")
create_table(data)
```

## Notable Incident: Parkland Shooting
A very notable mass shooting that occurred in 2018 was the Parkland mass shooting that occurred on `r parkland_date` in `r parkland_city` of `r parkland_state`. There were a total number of `r parkland_num_injured` people injured and they all died, resulting in `r parkland_num_killed` fatalities. 
For more information about the Parkland shooting, visit https://www.nbcnews.com/news/us-news/police-respond-shooting-parkland-florida-high-school-n848101

## Interactive Map of 2018 Shootings Across USA

This map provides details for every single mass shooting which has occurred in the USA in the year 2018. By clicking on the circles, you can view the city, the number of people killed, and the number of people injured in the shooting. The bigger the circle, the greater the number of people killed. 

```{r map, echo = FALSE}
cleaned_data_table <- read.csv("data/shootings_2018.csv")
create_map(cleaned_data_table)
```

Insights:
1. One thing I noticed was that the most deadly mass shootings seem to have occurred in coastal parts of the country such as the east coast, Florida, and California
2. Almost no mass shootings occurred in the middle-America region. 

## Plot

Question: I want to know which states had the highest death tolls as a result of mass shootings

```{r bar_graph, echo = FALSE}
cleaned_data_table <- read.csv("data/shootings_2018.csv")
make_bar_graph(cleaned_data_table)
```

Insights:
1. The state with the highest number of people killed by mass shootings overall was California
2. This data is interesting because although Florida had the highest number of people killed in a SINGLE mass shooting, it ranks 2nd in number of people killed by mass shootings overall
